Prospects of detecting gamma-ray emission from galaxy clusters: cosmic rays and dark matter annihilations

### 2011-06-13 paper.tex
text

@@

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
  \caption{\it }
 \label{fig:XCR}
\end{minipage}
\end{figure*}

>>>>

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
  \caption{\it Limits on the relative CR pressure, $\bra X_\rmn{CR}\ket = \bra
    P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$ averaged across the cluster. Our
    constraints are obtained with the extended Fermi-LAT limits in the energy
    range $E_\gamma=1-10$~GeV that assume a King profile which matches the
    extension of the thermal X-ray emission (black) and for comparison with
    Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
    computing those limits, we adopted our (conservative) analytic model
    \cite{2010MNRAS.409..449P} and a averaged relative CR flux as obtained from
    our simulations.}
 \label{fig:XCR}
\end{minipage}
\end{figure*}

@@
